\sloppy
\documentclass[12pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Luca Carbone - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Luca Carbone:  CV (Curriculum Vitae)},
            pdfauthor={Luca Carbone},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Luca Carbone}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{KU Leuven, Department of Mass Communication}
\moveleft.5\hoffset\centerline{Parkstraat 45 · 3000 Leuven · Belgium}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:lucacarbone.lc@gmail.com}{\nolinkurl{lucacarbone.lc@gmail.com}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +39 3478191290  \hspace{1 mm}      \faGlobe \hspace{1 mm} \href{http://www.lucacarbone.com}{\tt www.lucacarbone.com}   } 

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\emph{KU Leuven, BE} \hfill \begingroup\small 2020-2024\endgroup\\
DPhil Social Sciences - ERC starting grant\\
Supervisor: Laura Vandenbosch\\
\href{https://ercmimic.netlify.com/}{Project website}

\emph{Tilburg University, NL}
\hfill \begingroup\small 2017-2019\endgroup\\
M.Sc. (Res.) Social Sciences\\
Awarded best student, GPA 8.41/10, cum laude

\emph{University of Trento, IT}
\hfill \begingroup\small 2014-2017\endgroup\\
B.A. Sociology\\
GPA 28.74/30, 110 cum laude

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

\textbf{Carbone, Luca} .2019. ``Il mercato comunicativo su Twitter nelle
europee 2019.''" In: Valbruzzi, Marco (Ed.) \emph{L'Italia sovranista e
la sfida all'Europa. Le elezioni europee ed amministrative 2019}
(56-63). Bologna: Istituto Carlo Cattaneo. DOI: 10.31484/2611-5778\_41

\textbf{Carbone, Luca} .2019. ``Twitter come mercato comunicativo?
Un'analisi sulle europee 2019.'' In: Valbruzzi, Marco (Ed.)
\emph{L'Italia sovranista e la sfida all'Europa. Le elezioni europee ed
amministrative 2019} (65-73). Bologna: Istituto Carlo Cattaneo. DOI:
10.31484/2611-5778\_41 \newline

\hypertarget{work-in-progress}{%
\subsection{Work in progress}\label{work-in-progress}}

\textbf{Carbone, Luca} \& Achterberg, Peter: ````No room for thinking,
under the dome''. Flat earth and the boundary construction between
science and non- science on Twitter." \newline

\hypertarget{other-publications}{%
\subsection{Other Publications}\label{other-publications}}

Brusco, Sandro; \textbf{Carbone, Luca}; Miglino, Enrico; Tazzioli,
Agostino (2019, 30 May), Una semplice analisi econometrica del voto a
Più Europa del 2019 (A simple econometric analysis of the 2019 vote to
+Europe). Research report for NoiseFromAmerika. Available
\href{http://noisefromamerika.org/articolo/semplice-analisi-econometrica-voto-piu-europa-2019?fbclid=IwAR12kLTGJAonRf3Ctb-HlXYBGAspUhOSclDpQCg-mis-mDzM9vY8kZU21v8}{here}

\textbf{Carbone, Luca} (2019, 6 February), Il Dibattito Online
sull'Immigrazione in Italia (The Online Debate about Immigration in
Italy). Research report for Istituto Carlo Cattaneo. Available
\href{http://www.cattaneo.org/2019/02/06/il-dibattito-online-sullimmigrazione-in-italia/}{here}

\textbf{Carbone, Luca} (2018, 21 August), Sociology Journals and Network
Proprieties of the St.~Matthew Effect {[}blog post{]}. Available
\href{https://economicsociology.org/2018/08/21/sociological-journals-and-network-proprieties-of-the-st-matthew-effect/}{here}

\hypertarget{awards-funds}{%
\section{Awards \& Funds}\label{awards-funds}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

ERC starting grant scholarship (PhD fees + stipend).
\hfill \begingroup\small 2020-2024 \endgroup

University of Chicago, scholarship \& Dean's fellowship (\$31,500).
(declined) \hfill \begingroup\small 2019-2020 \endgroup

Tilburg University, visiting fund at Exeter University (€1000).
\hfill \begingroup\small June - August 2018\endgroup

\hypertarget{memberships-affiliations}{%
\section{Memberships \& affiliations}\label{memberships-affiliations}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Netherlands -- Flanders Communication Association (NeFCA).
\hfill \begingroup\small 2020-present\endgroup

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Day of Sociology, Amsterdam.
\hfill \begingroup\small 27th June 2019\endgroup

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Department of Sociology, Tilburg University
\hfill \begingroup\small March 2019 – September 2019\endgroup\\
Research assistant, Supervisor: Prof.~dr. Ruud Muffels\\
\emph{Research on basic income in the Netherlands.}

Research Institute Carlo Cattaneo, Bologna
\hfill \begingroup\small January 2019 – June 2019\endgroup\\
Research collaborator\\
\emph{Political discourses on Twitter.}

Research Institute IRVAPP, Trento
\hfill \begingroup\small February 2017 – May 2017\endgroup\\
Research internship, Supervisor: Dr.~Sonia Marzadro\\
\emph{Evaluation of social policies for the European project Youth
Guarantee.}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Department of Sociology, Tilburg University
\hfill \begingroup\small March 2017 – June 2017\endgroup\\
Teaching assistant\\
\emph{Course: Social Risk and Culture}

Department of Methodology \& Statistics, Tilburg University
\hfill \begingroup\small February 2017 – June 2017\endgroup\\
Teaching assistant\\
\emph{Courses: Introduction to Statistics, Questionnaire design,
Experimental design}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\hypertarget{programming-languages-softwares}{%
\subsection{Programming Languages \&
Softwares}\label{programming-languages-softwares}}

R (Advanced)\\
Markdown (Intermediate)\\
SPSS (Intermediate)\\
Stata (Basic) \newline

\hypertarget{languages}{%
\subsection{Languages}\label{languages}}

Italian (Native speaker)\\
English (Full professional proficiency)\\
Spanish (Elementary proficiency) \newline

\hypertarget{additional-training}{%
\subsection{Additional training}\label{additional-training}}

MOOC on ``Introduction to Agent-Based Modeling'', Santa Fe Institute
\hfill \begingroup\small October, 2019\endgroup\\
\emph{Agent-based modelling on NetLogo}

MOOC on ``Social and Economic Networks: Models and Analysis'',
\hfill \begingroup\small August, 2019\endgroup\\
Stanford University\\
\emph{Social network analysis}

Summer School at CWST Center, Leiden University
\hfill \begingroup\small August, 2018\endgroup\\
\emph{Scientometrics analysis}

Seminar on The Path to Quantitative Research, University of Trento
\hfill \begingroup\small 2016\endgroup\\
\emph{Factor analysis and counterfactual techniques for impact
evaluation} \newline

\hypertarget{social-causes}{%
\subsection{Social causes}\label{social-causes}}

Volunteering for Cultuur en Ontspanningscentrum
\hfill \begingroup\small April 2019 – June 2019\endgroup\\
\emph{The mission is to integrate sexual orientations, gender
identities, gender expression, and sex characteristics of sexual and
gender minority groups into the social norm through social activism,
education, support, and representation.}

Volunteering for ``L'Universitario''
\hfill \begingroup\small September 2016 – June 2017\endgroup\\
\emph{Founder of this university newspaper and director section
``Scientific Divulgation''.}

Volunteering for Arci
\hfill \begingroup\small June 2014 – July 2014\endgroup\\
\emph{Requalification of terrains confiscated to mafia with the project
``Campi della Legalità''.}

\hypertarget{references}{%
\section{References}\label{references}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Dr.~Laura Vandenbosch (KU Leuven)\\
Email address:
\href{mailto:laura.vandenbosch@kuleuven.be}{\nolinkurl{laura.vandenbosch@kuleuven.be}}

Prof.~dr. Peter Achterberg (Tilburg University)\\
Email address:
\href{mailto:P.Achterberg@tilburguniversity.edu}{\nolinkurl{P.Achterberg@tilburguniversity.edu}}

Dr.~Tim Reeskens (Tilburg University)\\
Email address:
\href{mailto:T.Reeskens@tilburguniversity.edu}{\nolinkurl{T.Reeskens@tilburguniversity.edu}}

Prof.~dr. Roger Leenders (Tilburg University)\\
Email address:
\href{mailto:R.T.A.J.Leenders@tilburguniversity.edu}{\nolinkurl{R.T.A.J.Leenders@tilburguniversity.edu}}

\end{document}

