\sloppy
\documentclass[12pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Luca Carbone - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Luca Carbone:  CV (Curriculum Vitae)},
            pdfauthor={Luca Carbone},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Luca Carbone}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{KU Leuven, Department of Mass
Communication}
\moveleft.5\hoffset\centerline{Parkstraat 45 · 3000 Leuven · Belgium}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:luca.carbone@kuleuven.be}{\nolinkurl{luca.carbone@kuleuven.be}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +32
16 37 24
05  \hspace{1 mm}      \faGlobe \hspace{1 mm} \href{http://www.lucacarbone.com}{\tt www.lucacarbone.com}   } 

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\emph{KU Leuven, BE} \hfill \begingroup\small 2020-2024\endgroup\\
Ph.D.~Social Sciences - ERC starting grant\\
Promoter: Laura Vandenbosch\\
PhD committee: Steven Eggermont, Giselinde Kuipers, Tom ter Bogt, Stef
Aupers, Michèle Lamont\\
\href{http://www.projectmimic.eu}{Project website}

\emph{Tilburg University, NL}
\hfill \begingroup\small 2017-2019\endgroup\\
M.Sc. (Res.) Social Sciences\\
Awarded best student, GPA 8.41/10, cum laude

\emph{University of Trento, IT}
\hfill \begingroup\small 2014-2017\endgroup\\
B.A. Sociology\\
GPA 28.74/30, 110 cum laude

\hypertarget{affiliations}{%
\section{Affiliations}\label{affiliations}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Department of Sociology, Harvard University
\href{https://sociology.fas.harvard.edu/people/luca-carbone}{profile}
\hfill \begingroup\small 2023-2024\endgroup

Weatherhead Cluster on Comparative Inequality and Inclusion, Harvard
University
\href{https://inequality.wcfia.harvard.edu/people/luca-carbone-0}{profile}
\hfill \begingroup\small 2023-2024\endgroup

\hypertarget{research-interests}{%
\section{Research interests}\label{research-interests}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

music; youths; resonance theory; success; meritocracy; masculinities;
role models; beliefs; mental health; computational social science;
content analysis; mixed-methods

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\hypertarget{peer-reviewed-articles}{%
\subsection{Peer-reviewed articles}\label{peer-reviewed-articles}}

\textbf{Carbone, L.}, \& Vandenbosch, L. (2024). Adolescents' Music
Tastes in the Streaming Era: The Case of Belgium. Cultural Sociology,
1--21. \url{https://doi.org/10.1177/17499755241244529/newline}

Noon, E. J., \textbf{Carbone, L.}, Swinnen, B., \& Vandenbosch, L.
(2024). Adolescents' videogame play, need satisfaction, and self-esteem:
A self-determination perspective. \emph{Current Psychology}.
\url{https://doi.org/10.1007/s12144-024-05933-6} \newline

Rosič, Jasmina, \textbf{Carbone, Luca}, Vanden Abeele, Mariek, Lobe,
Bojana, \& Vandenbosch, Laura. (2023). Measuring Adolescents' Digital
Well-Being in Everyday Life: The Perceived Digital Balance in
Adolescence Scale, \emph{Journal of Children and Media}.
\url{https://t.co/7KCSIGXBiW} \newline

\textbf{Carbone, L.} \& Vandenbosch, L. (2023). A Meta-Analysis of
Studies Examining the Effect of Music on Beliefs, \emph{Communication
Research}. \url{https://doi.org/10.1177/00936502231163633} \newline

Grusauskaite, K., \textbf{Carbone, L.}, Harambam, J., \& Aupers, S.
(2023). Debating (In) Echo Chambers: How People Read Conspiracy Theory
Videos On YouTube, \emph{New Media \& Society}.
\url{https://doi.org/10.1177/14614448231162585}. Finalist in the ICA
Popular Media \& Culture division's Top Paper Award in 2022 (out of 229
total papers). \newline

Rosič J., Janicke-Bowles S.H., \textbf{Carbone, L.}, Lobe B.,
Vandenbosch L. (2022). Positive Digital Communication Among Youth: The
Development and Validation of the Digital Flourishing Scale for
Adolescents, \emph{Frontiers Digital Health}.
\url{https://doi.org/10.3389/fdgth.2022.975557}. \newline

\textbf{Carbone, L.} (2022). Book Review: `Getting Signed: Record
Contracts, Musicians, and Power in Society.', \emph{New Media \&
Society}. \url{https://doi.org/10.1177/14614448221101210}. \newline

\textbf{Carbone, L.} \& Mijs, J. (2022). Sounds like meritocracy to my
ears: Exploring the link between inequality in popular music and
personal culture, \emph{Information, Communication \& Society}.
\url{https://doi.org/10.1080/1369118X.2021.2020870}. Pre-print available
\href{https://t.co/znOwdcxRO2?amp=1}{here}. Data, syntax, appendix, and
pre-registration available on \href{https://osf.io/5427t/}{OSF}.
Trending paper in Communication and Sociology Altmetrics on 10th January
2022 \href{https://t.co/6jLlFffvFT}{OOIR} \newline

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

Kuipers, Giselinde, Brans, Luuc, \textbf{Carbone, Luca}: ``The myth of
trickle down. How fashions do (not) spread in European fashion
magazines, and what this tells us about power and status in the global
fashion system'', Routledge.
(\url{https://books.google.be/books?id=t9DSEAAAQBAJ\&dq}) \newline

\textbf{Carbone, Luca} .2019. ``Il mercato comunicativo su Twitter nelle
europee 2019.'''' In: Valbruzzi, Marco (Ed.) \emph{L'Italia sovranista e
la sfida all'Europa. Le elezioni europee ed amministrative 2019}
(56-63). Bologna: Istituto Carlo Cattaneo. DOI: 10.31484/2611-5778\_41

\textbf{Carbone, Luca} .2019. ``Twitter come mercato comunicativo?
Un'analisi sulle europee 2019.'' In: Valbruzzi, Marco (Ed.)
\emph{L'Italia sovranista e la sfida all'Europa. Le elezioni europee ed
amministrative 2019} (65-73). Bologna: Istituto Carlo Cattaneo. DOI:
10.31484/2611-5778\_41 \newline

\hypertarget{work-in-progress}{%
\subsection{Work in progress}\label{work-in-progress}}

\textbf{Carbone, Luca}, Vandenbosch, Laura, \& Song, Hyunjin (Yonsei
University): ``The Sound of Meritocracy: A Content Analysis of
Meritocracy in Popular Music Lyrics Using a Semantic and Syntactic
Framing Approach'' (Under Review) \newline

\textbf{Carbone, Luca}, Alvarez-Cueva, Priscila (University of
Barcelona), \& Vandenbosch, Laura: ``Intersectional Representations of
Social Status in Popular Music Lyrics'' (Under review - major revisions)
\newline

Pirrone, Davide, \textbf{Carbone, Luca}, van Oosten, Annemarie (UVA), \&
Vandenbosch, Laura: ``From Affordance to Affair: Exploring the
Relationships between Online Sexual Activities and Online Infidelity
Behaviors'' (Under review) \newline

\textbf{Carbone, Luca}, Mijs, Jonathan (Boston University, Erasmus
University), Thijs van Dooremalen (Leiden University) \& Daedekindt,
Stijn (Ghent University): ``Towards a Sociology of Recurrent Events.
Constellations of Cultural Change around Eurovision in 18 Countries
(1981 -- 2021)'' (Under Review - major revisions) \newline

\textbf{Carbone, Luca}, Klimmt, Christoph (University of Hannover), \&
Vandenbosch, Laura: ``The Development of Music-Consistent Beliefs
through Identification and Similarity with Music Artists: A Biographic
Resonance Account'' (Under review) \newline

\textbf{Carbone, Luca}, Klimmt, Christoph (University of Hannover),
Schaap, Julian (Erasmus Univeristy of Rotterdam), \& Vandenbosch, Laura:
``Resonant Mediated Experiences: Towards an Integrated Approach of
Media-Psychological and Cultural Sociological Theories of Resonance''
(Drafting) \newline

\textbf{Carbone, Luca} \& Vandenbosch, Laura: ``The Development of
Music-Consistent Beliefs through Transportation with Music Narratives''
(Drafting) \newline

Noon, Edward (University of Leeds), \textbf{Carbone, Luca}, Swinnen,
Brent, Vandenbosch, Laura: ``Sending and Receiving toxic masculinity. A
study on videogame play and the videogame effects on adolescents'
performance pressure'' (Drafting) \newline

Antonucci, Lorenza (University of Birmingham), Sojka, Aleksandra Anna
(IE University), \textbf{Carbone, Luca}, Mijs, Jonathan (Boston
University): ``Meritocracy across European parties'' (Drafting) \newline

\textbf{Carbone, Luca}, Lamont, Michèle (Harvard University),
Vandenbosch, Laura: ``Cultural repertoires of success among European
youths. A daily diary study to disentangle the effects of music on
adolescents' success repertoires and mental health'' (Drafting) \newline

\hypertarget{other-publications}{%
\subsection{Other Publications}\label{other-publications}}

Brusco, Sandro; \textbf{Carbone, Luca}; Miglino, Enrico; Tazzioli,
Agostino (2019, 30 May), Una semplice analisi econometrica del voto a
Più Europa del 2019 (A simple econometric analysis of the 2019 vote to
+Europe). Research report for NoiseFromAmerika. Available
\href{http://noisefromamerika.org/articolo/semplice-analisi-econometrica-voto-piu-europa-2019?fbclid=IwAR12kLTGJAonRf3Ctb-HlXYBGAspUhOSclDpQCg-mis-mDzM9vY8kZU21v8}{here}

\textbf{Carbone, Luca} (2019, 6 February), Il Dibattito Online
sull'Immigrazione in Italia (The Online Debate about Immigration in
Italy). Research report for Istituto Carlo Cattaneo. Available
\href{http://www.cattaneo.org/2019/02/06/il-dibattito-online-sullimmigrazione-in-italia/}{here}

\textbf{Carbone, Luca} (2018, 21 August), Sociology Journals and Network
Proprieties of the St.~Matthew Effect {[}blog post{]}. Available
\href{https://economicsociology.org/2018/08/21/sociological-journals-and-network-proprieties-of-the-st-matthew-effect/}{here}

\hypertarget{awards-funds}{%
\section{Awards \& Funds}\label{awards-funds}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

University of Chicago, scholarship \& Dean's fellowship (\$31,500).
\hfill \begingroup\small 2019-2020 \endgroup\\
\emph{(declined due to insufficient financial resources to enroll in the
program)}

Tilburg University, visiting fund at Exeter University (€1,000).
\hfill \begingroup\small June-August 2018\endgroup

\hypertarget{invited-talks}{%
\section{Invited Talks}\label{invited-talks}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Talk ``Social media in the music industry'', Ancienne Belgique, Brussels
\hfill \begingroup\small 2024\endgroup

Seminar on Music and Meritoracy, BA Communication Sociology, University
of Vienna \hfill \begingroup\small 2024\endgroup

CII Spotlight, Weatherhead Center for International Affairs, Harvard
University \hfill \begingroup\small 2024\endgroup

Talk ``Meritocracy and Inequality'', Harvard Culture and Social Analysis
Workshop, Harvard University \hfill \begingroup\small 2024\endgroup

CII Seminar, Weatherhead Center for International Affairs, Harvard
University \hfill \begingroup\small 2024\endgroup

Graduate Seminar on Quantitative Methods in Sociology, Boston University
\hfill \begingroup\small 2024\endgroup

Current Research on Popular Music in Belgium (IASPM Benelux), Leuven
\hfill \begingroup\small 2023\endgroup

\hypertarget{conference-presentations}{%
\section{Conference Presentations}\label{conference-presentations}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

73rd conference of the International Communication Association (ICA),
Toronto \hfill \begingroup\small 2023\endgroup

Etmaal van de Communicatiewetenschap 2023, Enschede.
\hfill \begingroup\small 2023\endgroup

21st conference of the International Association for the Study of
Popoular Music (IASPM), Daegu. \hfill \begingroup\small 2022\endgroup

Day of Sociology, Groningen \hfill \begingroup\small 2022\endgroup

72nd conference of the International Communication Association (ICA),
Paris. \hfill \begingroup\small 2022\endgroup

Etmaal van de Communicatiewetenschap 2022, Brussels (online).
\hfill \begingroup\small 2022\endgroup

116th ASA Virtual Annual Meeting (American Sociological Association),
Chicago (online). \hfill \begingroup\small 2021\endgroup

7th International Conference on Computational Social Science IC2S2, ETH
Zürich (online). \hfill \begingroup\small 2021\endgroup

4th Joint Interdisciplinary Graduate Conference, Tilburg University
(online). \hfill \begingroup\small 2021\endgroup

IV Forum of Sociology (International Sociological Association), Porto
Alegre (online). \hfill \begingroup\small 2021\endgroup

Day of Sociology, Amsterdam. \hfill \begingroup\small 2019\endgroup

\hypertarget{professional-activities}{%
\section{Professional Activities}\label{professional-activities}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\hypertarget{academic-service}{%
\subsection{Academic Service}\label{academic-service}}

Chair session on Meritocracy, Alumni Conference, Weatherhead Center for
International Affairs, Harvard University.
\hfill \begingroup\small 2024\endgroup

Chair session on Class and Status at 21st IASPM Annual Meeting, Daegu,
South Korea. \hfill \begingroup\small 2022\endgroup

Presider roundtable cultural sociology (section on Meritocracy) at 116th
ASA Virtual Annual Meeting, online.
\hfill \begingroup\small 2022\endgroup

\hypertarget{occasional-reviewer}{%
\subsection{Occasional Reviewer}\label{occasional-reviewer}}

Journal for the Theory of Social Behaviour \newline American Behavioral
Scientist \newline Social Problems \newline Information, Communication,
\& Society \newline New Media \& Society

\hypertarget{memberships}{%
\subsection{Memberships}\label{memberships}}

International Association for the Study of Popular Music (IASPM).
\hfill \begingroup\small 2022-present\endgroup

International Communication Association (ICA).
\hfill \begingroup\small 2022-present\endgroup

Netherlands -- Flanders Communication Association (NeFCA).
\hfill \begingroup\small 2020-present\endgroup

KU Leuven Digital Society Institute (DigSoc).
\hfill \begingroup\small 2021-present\endgroup

KU Leuven Youth Institute.
\hfill \begingroup\small 2021-present\endgroup

American Sociological Association (ASA).
\hfill \begingroup\small 2021-2022\endgroup

\hypertarget{research-stays}{%
\subsection{Research stays}\label{research-stays}}

Research stay hosted by Prof.~Michèle Lamont at Harvard University.
\hfill \begingroup\small Spring 2024\endgroup

Research stay hosted by Prof.~Hyunjin Song at Yonsei University.
\hfill \begingroup\small July 2022\endgroup

Research stay hosted by Prof.~Eric Lybeck at Exeter University.
\hfill \begingroup\small June-August 2018\endgroup

\hypertarget{faculty-services}{%
\subsection{Faculty Services}\label{faculty-services}}

\emph{Co-Director} of MethLab\hfill \begingroup\small September
2020-present\endgroup\\
\emph{\href{https://soc.kuleuven.be/fsw/doctoralprogramme/meth-lab}{Meth-Lab}
is a bottom-up initiative created by Lala Muradova and Amélie Godefroidt
at KU Leuven for the sharing and presentation of novel methodological
techniques. As a co-director, I am responsible for contacting and
welcoming national and international speakers, the organization of the
meetings, the promotion of the events, and the management of finances.}

\emph{Member} of Diversity and Sustainability Commission at KU Leuven
(FSW)\hfill \begingroup\small April 2021 - September 2023\endgroup\\

\emph{Supervisor} MA thesis students:\newline - Sam
Samad\hfill \begingroup\small 2023-2024\endgroup\\
- Diana-Teodora Gaitan\hfill \begingroup\small 2022-2023\endgroup\\
- Dan Ding\hfill \begingroup\small 2022-2023\endgroup\\
- Maria Stefania Popa\hfill \begingroup\small 2022-2023\endgroup\\
- Ngoc Diep Nguyen\hfill \begingroup\small 2022-2023\endgroup\\
- Sarah Pans\hfill \begingroup\small 2021-2022\endgroup\\
- Kyra Bulinckx\hfill \begingroup\small 2021-2022\endgroup\\
- Hong Zhan\hfill \begingroup\small 2020-2021\endgroup\\

\emph{Supervisor} job students:\newline - Atri
Mukherjee\hfill \begingroup\small 2023\endgroup\\
- Bo Vanhoof\hfill \begingroup\small 2023\endgroup\\
- Tam Nguyen\hfill \begingroup\small 2022-2023\endgroup\\
- Rana Rafeh\hfill \begingroup\small 2022\endgroup\\
- Silke Vereeken\hfill \begingroup\small 2021\endgroup\\
- Annelies Rom\hfill \begingroup\small 2021\endgroup\\

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

School for Mass Communication Research, KU Leuven
\hfill \begingroup\small October 2021 -- present\endgroup\\
Teaching assistant\\
\emph{Course: Research Designs for Communication Science. Seminar name:
Computational methods for text analysis}

School for Mass Communication Research, KU Leuven
\hfill \begingroup\small November 2021 -- present\endgroup\\
Teaching assistant\\
\emph{Course: Media and Crisis. Seminar name: Social media: a curse or
blessing for the body image crisis?} \emph{Course: Media and Crisis.
Seminar name: Music and the cracks of individualism(?)}

Department of Sociology, Tilburg University
\hfill \begingroup\small March 2017 -- June 2017\endgroup\\
Teaching assistant\\
\emph{Course: Social Risk and Culture}

Department of Methodology \& Statistics, Tilburg University
\hfill \begingroup\small February 2017 -- June 2017\endgroup\\
Teaching assistant\\
\emph{Courses: Introduction to Statistics, Questionnaire design,
Experimental design}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Department of Sociology, Tilburg University
\hfill \begingroup\small March 2019 -- September 2019\endgroup\\
Research assistant, Supervisor: Prof.~Dr.~Ruud Muffels\\
\emph{Research on basic income in the Netherlands.}

Research Institute Carlo Cattaneo, Bologna
\hfill \begingroup\small January 2019 -- June 2019\endgroup\\
Research collaborator, Supervisor: Dr.~Marco Valbruzzi\\
\emph{Political discourses on Twitter.}

Research Institute IRVAPP, Trento \hfill \begingroup\small February 2017
-- May 2017\endgroup\\
Research internship, Supervisor: Dr.~Sonia Marzadro\\
\emph{Evaluation of social policies for the European project Youth
Guarantee.}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

\hypertarget{languages}{%
\subsection{Languages}\label{languages}}

Italian (Native speaker)\\
English (Full professional proficiency)\\
French (Intermediate proficiency) Spanish (Elementary proficiency)\\
\newline

\hypertarget{programming-languages-softwares}{%
\subsection{Programming Languages \&
Softwares}\label{programming-languages-softwares}}

R (Advanced)\\
Markdown (Intermediate)\\
Python (Intermediate)\\
Mplus (Basic)\\
HTML (Basic)\\
CSS (Basic) \newline

\texttt{chorrrds}: Music chords extraction - Collaborator\\
\emph{Available at: \url{https://CRAN.R-project.org/package=chorrrds}}

\hypertarget{additional-training}{%
\subsection{Additional training}\label{additional-training}}

Auditor ``Cultural Processes in the Production of Inequality''
(instructor: M. Lamont), Department of Sociology, Harvard University
\hfill \begingroup\small January-April, 2024\endgroup\\

Auditor ``Qualitative Social Analysis'' (instructor: M. Lamont),
Department of Sociology, Harvard University
\hfill \begingroup\small January-April, 2024\endgroup\\

Summer School Diversity in Arts, Culture and Media Studies, Erasmus
University Rotterdam \hfill \begingroup\small June, 2022\endgroup\\
\emph{Critical, feminist, and intersectional approaches}

Workshop PhD Media Psychology division of German Psychological
Association Conference, Aachen. \hfill \begingroup\small September
2021\endgroup\\

Essex Summer School in Social Science Data Analysis, Essex University
\hfill \begingroup\small August, 2020\endgroup\\
\emph{Mathematics}, \emph{Quantitative text analysis}

MOOC on ``Introduction to Agent-Based Modeling'', Santa Fe Institute
\hfill \begingroup\small October, 2019\endgroup\\
\emph{Agent-based modelling on NetLogo}

MOOC on ``Social and Economic Networks: Models and Analysis'',
\hfill \begingroup\small August, 2019\endgroup\\
Stanford University\\
\emph{Social network analysis}

Summer School at CWST Center, Leiden University
\hfill \begingroup\small August, 2018\endgroup\\
\emph{Scientometrics analysis}

Seminar on The Path to Quantitative Research, University of Trento
\hfill \begingroup\small 2016\endgroup\\
\emph{Factor analysis and counterfactual techniques for impact
evaluation} \newline

\hypertarget{references}{%
\section{References}\label{references}}

\vspace{-10pt}
\rule{1\linewidth}{\linethickness}

Available upon request.

\end{document}
